Generation of TypeScript Declaration Files from JavaScript Code

### 2021-05-21 mplr-2021/main.tex
Add manually added code example

To construct the type signature for a function, we inspect the
primitive types of each argument as well as the interface created from
interactions on the argument in the function body. We do the same for
the return type of the function. This procedure yields a candidate
type for each function call observed during the execution.
For instance, for the \lstinline{globToRegExp} examples shown in
Listing~\ref{code:code-example-extracted-motivating-example} we obtain
the following observed candidate types
\begin{verbatim}
globToRegExp : (glob: string, opts: undefined) -> RegExp
globToRegExp : (glob: string, 
                opts: { extended : bool,
                        globstar?: any,
                        flags?: any }) -> RegExp
\end{verbatim}
As the type for \lstinline{glob} and the return type
\lstinline{RegExp} are the same, we collapse the type for
\lstinline{opts} into a union type. The union with the
\lstinline{undefined} type is special and converted into an optional
argument so we arrive at a single collapsed candidate type
\begin{verbatim}
globToRegExp : (glob: string, 
                opts?: { extended : bool,
                         globstar?: any,
                         flags?: any }) -> RegExp
\end{verbatim}
We proceed in this way with merging further candidate types until we
reach a set of non-mergable types for the function. If this set
contains more than one candidate type, then we generate an overloaded
definition. For example, the candidate types
\begin{verbatim}
f(string): string
f(number): number
f(boolean): boolean
\end{verbatim}
cannot be merged as the return types are different. They give rise to
an overloaded definition with three alternatives. However, given the candidate types
\begin{verbatim}
g(string): string
g(number): string
g(boolean): boolean
\end{verbatim}
we can merge the first two types on the first argument (because all
remaining arguments and the return types are equal) by collecting \lstinline{string} and
\lstinline{number} into a union type. The resulting set of non-mergable types
is thus
\begin{verbatim}
g(string|number): string
g(boolean): boolean
\end{verbatim}

>>>>

To construct the type signature for a function, we inspect the
primitive types of each argument as well as the interface created from
interactions on the argument in the function body. We do the same for
the return type of the function. This procedure yields a candidate
type for each function call observed during the execution.
For instance, for the \lstinline{globToRegExp} examples shown in
Listing~\ref{code:code-example-extracted-motivating-example} we obtain
the following observed candidate types
\begin{verbatim}
globToRegExp : (glob: string, opts: undefined) -> RegExp
globToRegExp : (glob: string, 
                opts: { extended : bool,
                        globstar?: any,
                        flags?: any }) -> RegExp
\end{verbatim}
After expanding manually the code base with one particular case, we obtain the following type
\begin{verbatim}
re = globToRegExp("*/www/{*.js,*.html}", {
  flags: "i",
  globstar: true,
});

globToRegExp : (glob: string, 
                opts: { extended? : any,
                        globstar: bool,
                        flags: string }) -> RegExp
\end{verbatim}

As the type for \lstinline{glob} and the return type
\lstinline{RegExp} are the same, we collapse the type for
\lstinline{opts} into a union type. The union with the
\lstinline{undefined} type is special and converted into an optional
argument so we arrive at a single collapsed candidate type
\begin{verbatim}
globToRegExp : (glob: string, 
                opts?: { extended? : bool,
                         globstar?: bool,
                         flags?: string }) -> RegExp
\end{verbatim}
We proceed in this way with merging further candidate types until we
reach a set of non-mergable types for the function. If this set
contains more than one candidate type, then we generate an overloaded
definition. For example, the candidate types
\begin{verbatim}
f(string): string
f(number): number
f(boolean): boolean
\end{verbatim}
cannot be merged as the return types are different. They give rise to
an overloaded definition with three alternatives. However, given the candidate types
\begin{verbatim}
g(string): string
g(number): string
g(boolean): boolean
\end{verbatim}
we can merge the first two types on the first argument (because all
remaining arguments and the return types are equal) by collecting \lstinline{string} and
\lstinline{number} into a union type. The resulting set of non-mergable types
is thus
\begin{verbatim}
g(string|number): string
g(boolean): boolean
\end{verbatim}
